Tutorial_4

### 2025-07-08 Tutorial_4.Rmd
update Figure 9 (different linetypes)

```{r quick-summary-plot}
p3.1 <- ggplot(data_group, aes(x=timebin, y = outcome, colour = prime)) +
   geom_line(aes(group = prime)) + geom_point() +
   geom_jitter(data=data_pid, alpha = 0.5, width = 0.1, height = 0) +
   scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
   scale_x_discrete(labels = c(1:6)) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   labs(title = "Panis & Schmidt (2016) (N=6)",
        x = "time bins")
p3.1
```

@@

```{r plot-d1-prob}
p5.2 <- ggplot(d1_group, aes(x=bin, y = event, colour = condition)) +
   geom_line(aes(group = condition)) + 
   geom_point() +
   geom_jitter(data=d1_pid, alpha = 0.5, width = 0.1, height = 0) +
   scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
   scale_x_continuous(breaks = 1:bin_n, labels = 1:bin_n) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   labs(title = "event prob - simulation d1 (N=10)",
        x = "time bins")
p5.2
```

@@

```{r plot-d1-outcome}
p5.3 <- ggplot(d1_out_group, aes(x = bin, y = outcome, colour = prime)) +
  geom_line(aes(group = prime)) + 
  geom_point() +
  geom_jitter(data=d1_out_pid, alpha=0.5, width = 0.1, height = 0) +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
  scale_x_continuous(breaks = 1:bin_n, labels = 1:bin_n) +
  scale_colour_brewer(palette = "Dark2") +
  labs(title = "simulation d1 (N=10)",
       x = "time bins",
       y = "outcome")
p5.3
```

>>>>

```{r quick-summary-plot}
p3.1 <- ggplot(data_group, aes(x=timebin, y = outcome, colour = prime)) +
   geom_line(aes(group = prime, linetype = prime)) + geom_point() +
   geom_jitter(data=data_pid, alpha = 0.5, width = 0.1, height = 0) +
   scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
   scale_x_discrete(labels = c(1:6)) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   labs(title = "Panis & Schmidt (2016) (N=6)",
        x = "time bins")
p3.1
```

@@

```{r plot-d1-prob}
p5.2 <- ggplot(d1_group, aes(x=bin, y = event, colour = condition)) +
   geom_line(aes(group = condition, linetype=condition)) + 
   geom_point() +
   geom_jitter(data=d1_pid, alpha = 0.5, width = 0.1, height = 0) +
   scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
   scale_x_continuous(breaks = 1:bin_n, labels = 1:bin_n) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   labs(title = "event prob - simulation d1 (N=10)",
        x = "time bins")
p5.2
```

@@

```{r plot-d1-outcome}
p5.3 <- ggplot(d1_out_group, aes(x = bin, y = outcome, colour = prime)) +
  geom_line(aes(group = prime, linetype = prime)) + 
  geom_point() +
  geom_jitter(data=d1_out_pid, alpha=0.5, width = 0.1, height = 0) +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
  scale_x_continuous(breaks = 1:bin_n, labels = 1:bin_n) +
  scale_colour_brewer(palette = "Dark2") +
  labs(title = "simulation d1 (N=10)",
       x = "time bins",
       y = "outcome")
p5.3
```
